\sysfull

### 2018-04-17 paper/implementation.tex
impl: shorten

\textbf{Initialization.} The behavior of the API method
\texttt{COALA\_INIT} is very similar to \texttt{COALA\_NEXT\_TASK}, with the
addition that all the preliminary kernel initializations are performed inside
this function.

>>>>

\textbf{Initialization.} The behavior of the API method
\texttt{COALA\_INIT} is very similar to \texttt{COALA\_NEXT\_TASK}, with the
addition of performing preliminary kernel initializations, including hardware setup.
